\bf The Left Arm Bias in ITF Taekwon-Do Patterns \\ Chon-Ji to Juche

### 2011-01-02 article.tex
Removed directory example and rewrote tags section

  In a hierarchical and exclusive classification system, each object belong in
  one unambiguous category, which in turn is within another more general one.
  Take the hierarchy of folders in a computer file system, for example. If we
  want to organize articles on birds native to Africa in a directory, we have
  several options:

  \begin{lstlisting}
    1. ~/articles/birds
    2. ~/articles/africa
    3. ~/articles/africa/birds
    4. ~/articles/birds/africa
  \end{lstlisting}

  How we choose to organize the folders reflects a decision concerning the
  relative importance of each characteristic\cite{golder:ct}. Folder names and
  levels are in themselves informative, in that, like tags, they describe the
  information held within them\cite{jones:folders}.

  The directory structure of (1), and (2) make central the fact that the
  folders are about ``birds'' and ``africa''. But, they don't tell anything
  about the other category. In (3) and (4) the files are organized by both
  categories, and show that there is a parent-child or sibling relationships
  between the folder names\cite{mathes:folk}.

>>>>

  In a hierarchical and exclusive classification system, each object belong in
  one unambiguous category, which in turn is within another more general one.

  Take the hierarchy of folders in a computer file system, for example. How we
  choose to organize the folders reflects a decision concerning the relative
  importance of each characteristic\cite{golder:ct}.

  Folder names are in themselves informative, in that, like tags, they
  describe the information held within them\cite{jones:folders}. Furthermore,
  they way folder names relate to each other show a structural relationship
  between directories\cite{mathes:folk}.
